---
title: "Medical Cost Personal Datasets"
output: 
  github_document:
    toc: true
    toc_depth: 2
---

<style type="text/css">


h1.title {
  font-size: 22px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 20px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 18px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 14px;
  color: DarkBlue;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
```


# Introduction

## Dataset

The dataset used for this analysis is the medical cost personal dataset.The dataset provides key customer characteristics, such as age, sex, bmi and smoking status, and finally provides medical costs billed by health insurance for each individual. The ultimate aim is to accurately predict insurance costs using the variables in the dataset.

The data was obtained from Kaggle (https://www.kaggle.com/mirichoi0218/insurance).

## Objectives

The purpose of this analysis is to initially develop an understanding of the variables that influence the outcome variable 'charges' in the health insurance dataset. This will subsequently allow us to use our model to make predictions of customer charges based on key characteristics of the individual.

To do this we will use a linear regression model, moving from simple linear regression to multiple linear regression.

So two key questions to answer are:

1. Is there a significant relationship between any of the variables and customer charges?
2. Can the model be used to infer customer charges based on key variable values?

# Preliminary Analysis

Firstly, we will load any relevant libraries into R.

```{r, warning=FALSE, message=FALSE}

# Load libraries

library(tidyverse)

#install.packages("psych")

library(psych)

#install.packages("gmodels")

library(gmodels)

#install.packages("gridExtra")

library(gridExtra)

#install.packages("hrbrthemes", repos = "https://cinc.rud.is") # theme for ggplot2

#see https://github.com/hrbrmstr/hrbrthemes
library(hrbrthemes) # provides nice, clean theme for ggplot 

theme_set(theme_ipsum_rc())

#install.packages("summarytools")

library(summarytools)

library(MLmetrics)

#devtools::install_github("yeukyul/lindia")
library(lindia)

#install.packages("mctest")

library(mctest)
```

Next, we will load the data, and have a 'peak'.

```{r}

insurance_data <- read_csv("insurance.csv")

head(insurance_data)

```

We can see the key variables, age, sex, bmi, number of children, smoking status and region. The final variable is the insurance cost for that individual.

## Data Exploration

Initial data exploration is critical for a number of reasons, some of which being:

* Identify missing values and outliers. 
* Examine datatypes and distributions.

```{r}

str(insurance_data)


```

Looking at the above, we can see the data type associated with each variable, it may be necessary to alter some of these going forward. For example, to clearly mark variables such as smoker and region as categorical in R, we can change them to factors.

```{r}

summary(insurance_data)

```

The above summary table gives us an overview of each variable. For the numeric variables, we can see key descriptive statistics.

For the categorical variables, we can use the following function to get a more detailed overview of the content.

```{r}

gmodels::CrossTable(insurance_data$sex)

gmodels::CrossTable(insurance_data$smoker)

gmodels::CrossTable(insurance_data$region)


```

So we can see an equal split for gender and region, while the majority are non-smokers.

The above variables are clearly categorical. However, when we look at the 'children' variable, we can probably also describe this as categorical here, given there are distinct groups in the data, as shown below.

```{r}

gmodels::CrossTable(as.factor(insurance_data$children))


```

The distribution above confirm small sample sizes in groups 4 children and 5 children. Such small sample sizes may prove problematic when we build a regression model (for example, may result in very broad confidence intervals). It may therefore be prudent to group this variable into 0 - 2 children and 3 - 5 children.

```{r}

insurance_data <- insurance_data %>%
  mutate(
    children_group = case_when(
      children <= 2 ~ 0,
      children >= 3 ~ 1,
      TRUE ~ children
    )
  )

insurance_data$children_group <- as.factor(insurance_data$children_group)

head(insurance_data) # peak at the data
```

Above, we have coded individuals with 0 - 2 children as 0 and those with 3 - 5 as 1, then converted this variable into a factor. Categorising this way will make for easier interpretation of the regression model. We have done this while retaining the original variable of 'children', which will allow for comparison later.

At this point, we can also convert the other categorical variables into factors, so r knows to deal with them as such.

Categorical variables enter into statistical models differently than continuous variables, storing data as factors insures that the modeling functions will treat such data correctly.

```{r}
# As easy method to convert variables into factors

insurance_data$sex <- as.factor(insurance_data$sex)

insurance_data$smoker <- as.factor(insurance_data$smoker)

insurance_data$region <- as.factor(insurance_data$region)

insurance_data$children <- as.factor(insurance_data$children)

```

To make sure this has all worked as expected, we can check the structure of the dataset, as below.

```{r}

str(insurance_data)

```

At this point, we should also examine the distribution of the variables against charges. This will provide us with some early insight into key relationships in the data.

```{r, fig.height = 7, out.width= "100%" , fig.align = "center"}

plot_gender <- ggplot(data = insurance_data, mapping = aes(x = sex, y = charges)) +
  geom_boxplot(colour = "#1F3552", fill = "#4271AE", alpha = 0.7, outlier.color = "red",
               outlier.alpha = 0.2) +
  #ggtitle("Charges against Gender") +
  theme_ipsum_rc() +
  labs(x = "Gender", y = "Charges") +
  scale_y_comma()

#plot_gender

plot_children <- ggplot(data = insurance_data, mapping = aes(x = children, y = charges)) +
  geom_boxplot(colour = "#1F3552", fill = "#4271AE", alpha = 0.7, outlier.color = "red",
               outlier.alpha = 0.2) +
  #ggtitle("Charges against Number of Children") +
  theme_ipsum_rc() +
  labs(x = "Number of Children", y = "Charges") +
  scale_y_comma()

#plot_children

plot_smoker <- ggplot(data = insurance_data, mapping = aes(x = smoker, y = charges)) +
  geom_boxplot(colour = "#1F3552", fill = "#4271AE", alpha = 0.7, outlier.color = "red",
               outlier.alpha = 0.2) +
  #ggtitle("Charges against Smoking Status") +
  theme_ipsum_rc() +
  labs(x = "Smoking Status", y = "Charges") +
  scale_y_comma()
  # strong relationship here

#plot_smoker

plot_region <- ggplot(data = insurance_data, mapping = aes(x = region, y = charges)) +
  geom_boxplot(colour = "#1F3552", fill = "#4271AE", alpha = 0.7, outlier.color = "red",
               outlier.alpha = 0.2) +
  #ggtitle("Charges against Region") +
  theme_ipsum_rc() +
  labs(x = "Region", y = "Charges") +
  scale_y_comma() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

grid.arrange(plot_children, plot_gender, plot_region, plot_smoker, top = grid::textGrob("Categorical Variables - Against Charges", x = 0, hjust = 0))

```

The most apparent trend in the boxplots above, is the difference in charges between smokers and non-smokers. As would be expected, smokers incur higher medical insurance charges then non-smokers. This is an important finding for the determination of which variables to include in our final model.

Next, we can look at the distribution of continuous variables against charges. This is best done using scatter plots. The two continuous variables are age and BMI.

```{r, fig.align = "center"}

plot_age <- ggplot(data = insurance_data, mapping = aes(x = age, y = charges)) +
  geom_point(colour = "#4271AE") +
  theme_ipsum_rc() +
  labs(x = "Age", y = "Charges") +
  scale_y_comma()

#plot_age

plot_bmi <- ggplot(data = insurance_data, mapping = aes(x = bmi, y = charges)) +
  geom_point(colour = "#4271AE") +
  theme_ipsum_rc() +
  labs(x = "BMI", y = "Charges") +
  scale_y_comma()

#plot_bmi


grid.arrange(plot_age, plot_bmi, ncol = 2, top = grid::textGrob("Continuous Variables - Against Charges", x = 0, hjust = 0))
```

Although there is nothing as striking as the relationship between smoking and charges, we can firstly see in the BMI plot, perhaps the presence of two group.

It is difficult to discern a relationship from the age plot. However, there appears to be a slightly non-linear relationship between age and charges, shown by the slight curve in the distributions. 

The linear regression model assumes that there is a straight-line relationship between the predictors (x axis) and the response (y axis). Although only a slight curve, it is worth trying to resolve this.

A basic approach is to use non-linear transformations of the predictors, such as log X, √X, and X^2. Below, we will see the same plot, but age squared. 

```{r, fig.align = "center"}

ggplot(data = insurance_data, mapping = aes(x = age^2, y = charges)) +
  geom_point(colour = "#4271AE") +
  theme_ipsum_rc() +
  labs(x = "Age", y = "Charges") +
  scale_y_comma()

```

We can see the code now produces a chart with a straight line relationship between age and charges.

This will be useful later when we compare and contrast models. Therefore, we will add age^2 as a variable to our dataset...

```{r}

insurance_data <- insurance_data %>%
  mutate(
    age_sqr = age^2 
  )

```

Another way to look at the data, is the look at the relationship between the predictor variables themselves i.e. is the relationship between predictor 1 (x1) and outcome (y) dependent on the presence/influence of another predictor (x2). In short, perhaps the predictor variables are not independent of each other, in terms of their relationships with the outcome variable (y - in this case, charges).

For example, is the relationship between BMI and charges dependent on gender?

```{r}

plot_bmi_gender <- ggplot(data = insurance_data, mapping = aes(x = bmi, y = charges)) +
  geom_point(aes(colour = sex)) +
  labs(x = "BMI", y = "Charges") +
  scale_y_comma() +
  scale_color_ft()

plot_bmi_gender


```

The chart above doesn't indicate any interaction between gender and BMI, in terms of the relationship with charges.

A much clearer example is below.

```{r}

plot_bmi_smoking <- ggplot(data = insurance_data, mapping = aes(x = bmi, y = charges)) +
  geom_point(aes(colour = smoker)) +
  theme_ipsum_rc() +
  labs(x = "BMI", y = "Charges") +
  scale_y_comma() +
  scale_color_ft()

plot_bmi_smoking

```

This plot strongly indicates an interaction between BMI and smoking status. This can be explained as follows: *The relationship between BMI and charges is strongly dependent on the individuals smoking status. For a smoker, as BMI increases the health insurance charge also increases. However, for a non-smoker, as BMI increases, no such relationship seems to exist - charges do not increase.*

This will be important when we build our model. Indeed, we can account for this interaction in our model, which will be described later.

Given the small number of variables in this data, it was possible to work through them individually. However, we can use a matrix to visualise relationships between multiple variables. A number are available. One example being the 'pairs.panels' from the library psych. Such a plot allows us to visualise numerous correlations and plots in one go.

```{r, fig.height = 7, out.width= "100%"}

psych::pairs.panels(insurance_data,
                    method = "spearman",
                    hist.col = "purple",
                    density = TRUE,
                    ellipses = FALSE)

```

## Story so Far

Our analysis so far has allowed to us determine the general distribution of the predictor variables. This in turn has allowed us to identify variables with unbalanced distributions, such as number of children, and a variable with a slightly non-linear relationship with charges, age. We therefore created some new variables to address these issues. No doubt we could create additional variables, further grouping and refining our existing variables, but we will stick to what we have for now, and add additional ones going forward if needed.

We also explored some key interactions between some of the predictor variables. This identified a key relationship between smoking status and BMI, where the increase in charges with increasing BMI was dependent on smoking status.

Together, these factors will help shape our linear regression model.

# Simple Linear Regression

Linear regression is a simple approach for supervised learning. In particular, it is useful for predicting a quantitative response.

Correlation is a measure of the strength of the relationship between two variables. 
But more often we want to be able to *describe and quantify the relationship between two variables,* and linear regression allows us to do this.

*The ultimate aim is to use one variable to predict another*

The outcome variable is always put on the y-axis and the predictor on the x-axis.

These terms can be used, but often hear them referred to as independent and dependent variables. 

In this case, the outcome variable is quite obvious - individual medical costs, *charges*.

So we are going to quantify a relationship between predictor variable(s) and outcome variable by fitting a straight line to the data. *But we want to make sure we fit an optimal straight line*
The are many methods to find a line of best fit, but the standard approach to use is called least squares regression.

This approach fits a regression line that minimises the sum of the squared vertical distances between the observed value and the fitted line. The distances are called residuals. Residuals are calculated by subtracting the predicted value from the observed value. 

The formula for a straight line is:

$$y = \alpha + \beta X $$

When x is zero, you will see from the equation that y will just equal alpha - as the beta term will disappear.

This means that alpha is the value of y where the regression line cuts the y-axis.

And beta is the slope of the line.

$$\alpha = (y) intercept$$

$$\beta = slope of the line$$
We will demonstrate this using an example, with an explanation of the results.

Before fitting the model, we will split the data into training and test data sets. This will allow us to develop our models using the training data, and test the model using the test data.

```{r}

set.seed(100)  # setting seed to reproduce results of random sampling

trainingRowIndex <- sample(1:nrow(insurance_data), 0.8*nrow(insurance_data))  # row indices for training data

trainingData <- insurance_data[trainingRowIndex, ] #model training data


testData  <- insurance_data[-trainingRowIndex, ]   # test data


```


Now lets build a simple linear regression model using 1 variable. Given we suspect smoking status has a strong relationship with charges based on our exploratory analysis, we will use smoking as the predictor variable.

```{r}

lm_simple <- lm(charges ~ smoker, data = trainingData)

# use summary to look at the results

summary(lm_simple)

# look at confidence intervals 

confint(lm_simple)

```

The first item of interest above is labelled intercept. **This is the value of alpha.** Another value we are interested in is labelled smokeryes - **this is our beta estimate**. And it is 23123.9. If we look along this row, we will see the p value for beta, which is 2e-16 (2.2 X 10 ^ -16), which is extremely small. 

To put this into context, for a one unit increase in our predictor, smoking status, it is estimated that charges increase by $23,123.90. This is how you interpret the beta coefficient in the model of interest.

Another important thing to note, is that the variable smoking is categorical (a factor in r). What the model is doing is comparing the mean charge for 'yes' against the reference category, which in this case is 'no' i.e. moving from no to yes in terms of smoking status increases the charges on average by $23,123.90.

Furthermore, the very small p value allows us to reject the null hypothesis of no relationship between the predictor and the outcome variable.

*The null hypothesis is whether the population parameter is 0. For beta, if there is a 0 slope, then there is no relationship between the predictor and the outcome. Here the p value is very small, so the evidence against a null hypothesis is strong.*

Given this, we can see that the equation could potentially be used to predict the outcome variable.

charges =  8555.1 + 23,123.9 x smoker

*It would have been better to recode 'smoker' as 0 (no) and 1 (yes) - this makes it easier to interpret the equation.* For example, if not a smoker, the predicted charge is simply $8,555.10 (as 23,123.9 x 0 = 0).


The assess the goodness of fit to this model, we look at the R-squared and the adjusted R-squared values. How much variation does this model explain? 
**You can see that the adjusted R-squared value is 0.61 meaning the model is explaining around 61% of the total variability in the observed data.** 

A brief explanation of the R-squared value is as follows:

The regression line will explain a proportion of the variability in the data, and the residuals indicate how much variability is left unexplained after we fitted the regression line. Therefore R squared is measure of how much variability is explained by the model as a proportion of the total variability of the data. As a consequence R^2 is a value between 0 and 1.

The adjusted R-squared penalises for the number of predictor variables included in the model. Therefore, it's a better measure to compare our models with - which is more relevant later for our multiple linear regression models.

Overall, the model confirms a significant relationship between smoking status and charges...

```{r}

ggplot(data = insurance_data, mapping = aes(x = smoker, y = charges)) +
  geom_point(colour = "#4271AE") +
  theme_ipsum_rc() +
  labs(x = "Smoker", y = "Charges") +
  scale_y_comma()

```
 
# Multiple linear regression 

Next we will extend our simple linear regression model into a multiple regression model. The first thing we need to decide is what variables to include as out predictor. Given the number of variables in this dataset is small, we could investigate some of the relationships individually, as we did earlier, and this allows us make informed decisions about which variables to include.

We need to be careful not include too many variables, as we may risk overfitting the model. This occurs when there are too many variables included and the model fits the data too closely. We end up just explaining random error, rather than real relationships.

However, we also need enough variables to allow the model parameters to be appropriately estimated.

There are some automated methods available to select variables, which are sometimes used when there are a large number. Examples include forward selection, backward selection and a setpwise approach. These add variables step by step, only keeping those that achieve a certain criteria. However, it is often better to select variables based on published literature, which have confirmed known relationships, as well as your own findings as an investigator.

For example, from our analysis earlier, we could see that smoking is strongly relation with charges, and this also had a bearing on the relationship between BMI and charges. In addition, it is not unreasonable to think that insurance charges will increase with age. This then gives a starting point up to build a model with.

```{r}

lm_multiple_v1 <- lm(charges ~ bmi + smoker + age, data = trainingData)


summary(lm_multiple_v1)

```

Our first model included BMI, smoking status and age as predictor variables, and the model was able to explain 73% of the variation in the data, shown by the adjusted R-squared. In addition, all three of our variables have reached significance, meaning they are significantly related to the outcome variable, charges.

However, if we remember from our analysis we noted there was a strong interaction between smoking status and BMI:

```{r}

plot_bmi_smoking
```


Our first multiple regression model assumed the two variables BMI and smoker are independent and additive. However, this assumption may not hold, and the presence of both conditions may interact to have a different impact on the outcome. We can see this in the chart above, where the relationship between BMI and charged is dependent on smoking status. For a smoker, as BMI increases, so do charges. We can account for this interaction using an interaction term in our model. We do this by simply including an additional term, **multiplying the variable BMI by smoker.**

In addition to our analysis with BMI and smoker, we also applied a transformation to the age variable, to produce a linear relationship between age and charges. We will also include this in the model.

```{r}

lm_multiple_v2 <- lm(charges ~ age_sqr + bmi*smoker, data = trainingData)

summary(lm_multiple_v2)

```

The new model has a greater Adjusted R squared value, and the interaction term of bmi and smoker is highly significant, confirming that the true relationship is not additive (not independent).

Another transformation we added to the data was the grouping of number of children. This was due to the small sample sizes in the 4 and 5 children group. We can add this in to determine if it improves the model. We coded this variable as 0 for 0-2 children and 1 for 3-5 children.

```{r}

head(trainingData)

lm_multiple_v3 <- lm(charges ~ age_sqr + bmi*smoker + children_group , data = trainingData)

summary(lm_multiple_v3)

```

The new addition is just about significant, and means we can reject the null hypothesis of no relationship. In addition, the Adjusted R Squared has marginally increased.

We can use the anova function in r to compare models v2 and v3 to determine if there is a significant difference between the two. The anova() function performs a hypothesis test comparing the two models. The null hypothesis is that the two models fit the data equally well, and the alternative hypothesis is that the model with 'children_group' is superior. 

```{r}

anova(lm_multiple_v2, lm_multiple_v3)

```

This confirms that the third model is marginally better, and has reached significance over the second model without 'children_group'.

We will therefore use this as our final model to make our predictions with.

## Collinearity

When developing a multiple linear regression model, it is important to assess for a phenomenon called collinearity. This relates to the relationship between the predictor variables. So in practice, variables are often correlated to some extent, but if the correlation between two predictors is strong, this can cause a problem when modelling - this is known as collinearity and it refers to a strong linear relationship between two predictors. It causes a problem because the two variables are both explaining the same variance in the observations, which means the variance can't be separated between these two competing predicates.

When you have multiple predictors that collerate, this is called multicollinearity. To detect this in a model, we can look at the variance inflation factor (VIF), which estimates how much the variance of a regression coefficient is inflated due to multicollinearity in the model.

In r, it is possible to obtain the VIF for each predictor can be obtained as follows:

```{r}

mctest::imcdiag(model.matrix(lm_multiple_v3)[,-1], lm_multiple_v3$model[1], method = "VIF")


```

The test above gives a VIF score for each predictor. A score of 1 is considered to indicate no correlation. There are no set rules for what indicates high correlation, but typically, anything above 5 or 10 may be considered high. We have a very high VIF for the bmi:smoker interaction term and smoker variable, although this is to be expected given we added this interaction term to the model. 

## Predictions

Now lets predict some costs based on our test data.

```{r}

ChargesPredict <- predict(lm_multiple_v3, testData)  # predict charges


```

To test the accuracy of our model, a simple correlation between the actual and predicted values can be used to provide an indication.

```{r}

actuals_vs_preds <- data.frame(cbind(actuals=testData$charges, predicteds=ChargesPredict))

correlation_accuracy <- cor(actuals_vs_preds) 

correlation_accuracy

```

There is a strong correlation between the two: 94%, which is good. We can also use the Root Mean Squared Error (RMSE) to assess the accuracy of the model. This represents the average difference between the observed known outcome values in the test data and the predicted outcome values by the model. The lower the RMSE, the better the model.

```{r}



RMSE(ChargesPredict, testData$charges)


```

This value should be interpreted in context of the outcome variable, charges. We can see the range of values below:

```{r}

ggplot(data = insurance_data, mapping = aes(x = charges)) + 
  geom_histogram(fill = "#4271AE") +
  scale_x_comma() 


```

Given the broad range of costs, the RMSE of 4440.12 doesn't seem too unreasonable.

### Example Case

We can now try to enter some case data into the model, as follows:

```{r}

newdata <- data.frame(
  age_sqr = 70^2,
  children_group = as.factor(1),
  smoker = factor("yes"),
  bmi = 20
)

predict(lm_multiple_v3, newdata = newdata)

```


# Model Diagnosis

There are a number of assumptions that should be assessed for a linear regression model. This type of model is a referred to as a parametric test, which make a number of assumptions about the underlying data. The assumptions can be defined as follows:

* Linearity between outcome (y) and predictor (x) - relationship is approx. linear between predictor and outcome variables.
* For each value of the predictor variable, the outcome variable follows a normal distribution. 
* Assume that the variance is constant for each value of the predictor.

To determine whether these assumptions hold, we examine the residuals in the model (residuals are distances between the observed values and the fitted regression line).

**If the assumptions we described hold, then the distribution of the residuals will be normal with a mean of zero and a constant variance across the predictor values.**

We can check the assumptions of normally distributed residuals using a Quantile-Quantile (Q-Q) plot. The Q-Q plot is a plot of the quartiles of the residuals against the quartiles of a theoretical normal distribution - if the residuals are normal then the observations will lie on a straight line.

Below we will create a Q-Q plot from data we know are normally distributed, so we know what a Q-Q plot would look ideally look like. Note, the plot below is taken from this tutorial: https://www.storybench.org/diagnosing-the-accuracy-of-your-linear-regression-in-r/

```{r}


NormalData <- data.frame(
  norm_x = stats::rnorm(n = 1000, mean = 0, sd = 1),
  norm_y = stats::rnorm(n = 1000, mean = 1, sd = 3)
)

ggNormQQPlot <- NormalData %>%
  # name the 'sample' the outcome variable (norm_y)
  ggplot(mapping = aes(sample = norm_y)) +
  # add the stat_qq_band
  qqplotr::stat_qq_band(
    bandType = "pointwise",
    mapping = aes(fill = "Normal"), alpha = 0.5,
    show.legend = FALSE
  ) +
  # add the lines
  qqplotr::stat_qq_line() +
  # add the points
  qqplotr::stat_qq_point() +
  # add labs
  ggplot2::labs(
    x = "Theoretical Quantiles",
    y = "Sample Residuals",
    title = "Normal Q-Q plot for Simulated Data"
  )

ggNormQQPlot
```

The focus on the plot above should be on the middle section, where we can see the points sit on the line. You should always expect to see some drift in the tails of a distribution of a Q-Q plot, as we can see above.

In order to assess the assumption of constant variance across the predictor (homogeneity of variance), then a useful plot is to view the residuals by the fitted regression values, or the predictive variable. In this plot, the residuals are on the y-axis, and the fitted values from the regression line are on the x-axis. What this should show you is an equal scatter of residual values around the mean value of zero. What you don't want to see is variability in the scatter.

To assess these assumptions in our multiple regression model, the quickest function to use is plot(). This generates a number of diagnostic plots, with which we can diagnose our model.

```{r}

plot(lm_multiple_v3)

```

There is also a package called lindia, which includes a function calles gg_diagnose(), which produces a large number of diagnostic plots. Otherwise, you can produce just the ones required:

```{r}


final_QQ <- lindia::gg_qqplot(lm_multiple_v3)

final_resfit <- lindia::gg_resfitted(lm_multiple_v3)

#final_spread <- lindia::gg_scalelocation(lm_multiple_v3)

#grid.arrange(final_QQ, final_resfit, ncol = 2, top = grid::textGrob("Q-Q Plot and Residuals Against Fitted", x = 0, hjust = 0))

final_QQ

final_resfit

```

The diagnostic plots have therefore revealed some issues with our model. Firstly, the Q-Q plot indicates the residuals are not normally distributed. In addition, the residual vs fitted value plot is not equally spread out. There are a large cluster of points to the left. This reflects a lack of a linear relationship between our predictors and the outcome variable in our model. In addition, data are homoscedastic if the variance is the same across all values of predictor variables, we can see from the scale-location plot (produced by plot()), that this isn't the case.

# Conclusion

In conclusion, we produced a model that was able to explain approximately 83% of the variance in our data. In addition, our test data confirmed a strong correlation between predicted and actual values, indicating the model has some effectiveness as a predictive model. However, upon diagnosis, we identified some issues with assumptions around our underlying data. 

Next steps could include investigating further potential transformation in the data, to improve the distributions of the residuals. In addition, the use of an alternative type of model may also be more appropriate for this type of data.

